---
title: "hw2"
author: "Manqing Lin"
format: pdf
editor: visual
---

## Problem1

##a&b&c

version1:

```{r}
#| code-fold: true
#| code-summary: "Show the code"

## define a function call play_dice
play_dice<-function(x){
## set an initial total win or loss as the cost to play the game
  ttwin<--2
## run the loop in the range of 1 and number of dice to roll
  for(i in 1:x){
## randomly generate a number between 1 to 6
    set.seed(567)
    result<-sample(1:6, 1, replace=TRUE)
## if the roll result is 2, we get $2
    if(result==2){
      ttwin=ttwin+2
    }
## if the roll result is 4, we get $4
    if(result==4){
      ttwin=ttwin+4
    }
## if the roll result is 6, we get $6
    if(result==6){
      ttwin=ttwin+6
    }
## we lose the when we on a roll of 1, 3 or 5
    ttwin=ttwin
  }
## return the total winnings or loses
  return(ttwin)
}

## test the function with different input
play_dice(3)
play_dice(3000)

```

version2:

```{r}
#| code-fold: true
#| code-summary: "Show the code"
## define a function call play_dice
play_dice<-function(x){
## set an initial total win or loss as the cost to play the game
  ttwin<--2
## run the loop in the range of 1 and number of dice to roll
  for(i in 1:x){
## randomly generate a number between 1 to 6
    set.seed(567)
    result<-sample(1:6, 1, replace=TRUE)
## use the built-in R function "ifelse" to define the win or lose for each dice
    win<-ifelse(result%%2==0,result,0)
## total win or lose will be the sum of the initial cost to play the game and the roll value of each dice
    ttwin=ttwin+win
  }
## return the total win or lose
  return(ttwin)
}
## test the function with different input
play_dice(3)
play_dice(3000)

```

version3:

```{r}
#| code-fold: true
#| code-summary: "Show the code"
## define a function call play_dice
play_dice<-function(x){
  ttwin<--2
  result<-c()
  
    for(i in 1:x){
      ## randomly generate a number between 1 to 6
      set.seed(567)
      result[i]<-sample(1:6, 1, replace=TRUE)
    }
    roll_table<-table(result)
    rowval1<-as.numeric(names(roll_table))
    rowval2<-as.numeric(roll_table)
    dicenum<-ifelse(rowval1%%2==1,0,rowval1)
    ttwin<-ttwin+sum(dicenum*rowval2)
    return(ttwin)
}

play_dice(3)
play_dice(3000)

```

version4:

```{r}
#| code-fold: true
#| code-summary: "Show the code"
play_dice<-function(){
  
  set.seed(567)
  result<-sample(1:6, 1, replace=TRUE)
  if(result%%2==0){
    win<-result
  }
  else{
      win<--2
    }
  return(win)
}

num<-3
ttwin<-sapply(1:num, function(x)play_dice())
sum(ttwin)

```

##d

```{r}
install.packages("microbenchmark")
library(microbenchmark)
```

```{r}
microbenchmark(num_100=play_dice(100),num_10000=play_dice(10000))
```

The time used for play 10000 dice games is longer than the tine use for play 100 dice games. It does make sense since there is a loop in the "play_dice" function, and it will need to run 100 and 10000 times separately.

## Problem2

##a

```{r}
#| code-fold: true
#| code-summary: "Show the code"

library(readr)
cars <- read_csv("~/Desktop/cars.csv",show_col_types = FALSE)
##View(cars)

names(cars)<-c("H","L","W","Driveline","EngineType","IfHybrid","#Gears","Transmission","citympg","fueltype","highwaympg","classification","ID","make","model year","year","horsepower","torque")

```

##b

```{r}
#| code-fold: true
#| code-summary: "Show the code"

cars1<-subset(cars,fueltype=="Gasoline")

```

##c

```{r}
#| code-fold: true
#| code-summary: "Show the code"

mod1<-lm(highwaympg~horsepower+torque+H+L+W+year,cars1)
summary(mod1)
```

Since the estimated coefficient of horsepower is greater than 0, the horsepower is positively correlated to the highway mileage. On average, a unit increase in the horsepower is associated with an estimated of 0.0182 miles change in the highway mileage.

##d

```{r}
mod2<-lm(highwaympg~horsepower*torque,cars1)
summary(mod2)
plot_model(mod2, type="int",mdrt.values = "meansd")
```

##e

```{r}
Y=matrix(cars1$highwaympg, ncol=1)
X = cbind(rep(1,length(Y)),cars1$horsepower,cars1$torque,cars1$H,cars1$L,cars1$W,cars1$year)

solve(t(X)%*%X, t(X)%*%Y)
```
